---
title: "<center><b>Happiness Around the World</b></center>"
author: "<center><b>Lu, Brauchle, Kolinko</b></center>"
output:
  html_notebook:
    toc: yes
  html_document:
    self_contained: no
    toc: yes
---

#**Introduction**
This project shows interesting findings about the correlation between happiness (rated on a scale from 1-10) and its relationship between various employment sectors in countries around the world. 

Our data was supplied from the [International Labour Organization](http://www.ilo.org/global/research/global-reports/global-employment-trends/2014/WCMS_234879/lang--en/index.htm), [Kaggle](https://www.kaggle.com/unsdsn/world-happiness),
[UN](http://www.un.org/en/development/desa/policy/wesp/wesp_current/2014wesp_country_classification.pdf), [Google Developers](https://developers.google.com/public-data/docs/canonical/countries_csv), and [World Bank](http://data.worldbank.org/indicator/SP.POP.TOTL)

#**R Configuration**
Below we display our sessionInfo().

```{r sessionInfo}
sessionInfo()
```

#**The Data**

```{r}
source("../01 Data/preETL_happiness_jobs.R")
```

**The Visualizations**
...


